Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-02-27 presentation-plan/Plan_presentation_monday.tex
Add bibtex, explain STRIPS from the 1970s

\begin{itemize}
	\item STRIPS
\end{itemize}

@@

>>>>

\begin{itemize}
	\item STRIPS \cite{fikes1971strips}
\end{itemize}

\subsubsection{STRIPS}

STRIPS~\cite{fikes1971strips} is a influential method of defining planning
problems.

Take for example~\ref{fig:strips}. R is the robot, B and C are two objects at
places a, b and c. The goal is to achieve the configuration such that B is at
place k and in which C is not at place c. The robot can move to an object and
it can push objects to another position.

\begin{figure}[htb]%
\includegraphics[width=0.8\columnwidth]{strips-example.pdf}%
\caption{Configuration of objects and robot for example problem (Figure from~\cite{fikes1971strips})}%
\label{fig:strips}%
\end{figure}

The goal could be written as

\[
	(\exists s) [ AT(B,k,s) \land \neg AT(C,c,s) ]
\]

If we find an instance of s, the problem is solved.

STRIPS also defines operators. In this instance examples can be \texttt{goto}
and \texttt{push}.

\begin{description}
	\item[push(u,x,y)] Robot pushes object \texttt{u} from \texttt{x} to
		position \texttt{y}
	\begin{description}
		\item[Precondition:] $(\exists s) [AT(u,x,s) \land ATR(x,s)]$
		\item[Delete list:] $\{AT(u,x,s), ATR(x,s)\}$
		\item[Add list:] $\{AT(u,y,push'(u,x,y,s^*)), ATR(y,push'(u,x,y,s^*))\}$
	\end{description}
	\item[goto(x,y)] Robot goes from place \texttt{x} to \texttt{y}
	\begin{description}
		\item[Precondition:] $(\exists s) [ATR(x,s)]$
		\item[Delete list:] $\{ATR(x,s)\}$
		\item[Add list:] $\{ATR(y,goto'(x,y,s^*))\}$
	\end{description}
\end{description}

The initial world model can be described by:

\[
	s_0 : \{ ATR(a,x_0), AT(B,b,s_0), AT(C,c,s_0) \}
\]

Besides that there is a global requirement that two blocks cannot be at the
same position at any time.

\paragraph{Problems}

\begin{itemize}
	\item How to efficiently store nodes (states) of the world.~\cite{fikes1971strips}.
	\item ...
\end{itemize}

@@

\bibliographystyle{plain}
\bibliography{Plan_presentation_monday}
